\documentclass[10pt,a4paper,withhyper]{altacv}

\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}
\usepackage{paracol}


\usepackage[default]{opensans}

% Colours
\definecolor{Main}{HTML}{000000}
\definecolor{Accent}{HTML}{226a60}
\definecolor{LightAccent}{HTML}{226a60}
\colorlet{heading}{Main}
\colorlet{tagline}{LightAccent}
\colorlet{headingrule}{Accent}
\colorlet{accent}{LightAccent}
\colorlet{emphasis}{Main}
\colorlet{body}{Main}

\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}

\begin{document}
\name{Hannah Mowbray}
\tagline{Full Stack Software Engineer}
\personalinfo{
  \email{hannahmowbray2@gmail.com}
  \phone{+44 7900 033775}
  \location{Edinburgh, Scotland}
  \linkedin{hannah-mowbray-036505212}
  \github{hmowbray2}
}

\makecvheader

\AtBeginEnvironment{itemize}{\small}
\columnratio{0.6}
\begin{paracol}{2}

% --- Left column ---
\cvsection{Experience}

\cvevent{Software Engineer}{Lloyds Banking Group}{2024 -- current}{Edinburgh}
\begin{itemize}
  \item Deployed a pension transfer tracker into production with over 10,000 customer uses in the first month.
  \item Presented to the Engineering Leadership Team including the CIO of Scottish Widows.
  \item % TODO: confirm/adjust — built and maintained services running on Kubernetes, provisioning cloud infrastructure with Terraform on Google Cloud.
  Built and maintained containerised services on Kubernetes, using Terraform to provision and manage supporting Google Cloud infrastructure.
  \item % TODO: confirm/adjust — tailor to your actual AI/agent work at Lloyds
  Contributed to internal AI agent tooling, including retrieval-augmented generation (RAG) systems for enterprise use cases.
  \item % TODO: confirm/adjust — add a scale/ownership bullet, e.g. team size, services owned, on-call, etc.
  Collaborated across cross-functional teams to design and deliver scalable, testable full-stack features from requirements through to production.
  \item Lead a team of four engineers, representing the team in daily cross-team lead catch-ups and holding sign-off responsibility for release documentation ahead of production deployments.
\end{itemize}


\cvsection{Projects}


\cvevent{Folio}{Personal Project}{2026}{}
\begin{itemize}
  \item Building a white-labelled RAG-powered chatbot SaaS product for UK accountancy practices, architected across three services (API, UI, docs) on a lean, cost-constrained stack.
  \item Integrated Clerk auth, Stripe billing, Pinecone vector search and Voyage AI embeddings with Claude for retrieval-augmented chat.
\end{itemize}

\divider

\cvevent{Booking System UI}{Dales Cycles Workshop - Freelance}{2025}{}
React + TypeScript UI built from scratch with Vite, integrating with a .NET API and Postgres DB.

\divider

\cvevent{Octobot}{Personal Project}{2024}{}
Python + Playwright bot deployed to Google Cloud using Cloud Run and Cloud Scheduler.




\switchcolumn

% --- Right column ---

\cvsection{Education}

\cvevent{PhD Researcher}{University of Glasgow}{2022 -- 2024}{Glasgow}
\begin{itemize}
  \item Focused on Python automation for semiconductor mask design, improving workflow throughput.
\end{itemize}

\divider

\cvevent{MSci Chemistry}{University of Nottingham}{2018 -- 2022}{Nottingham}
\begin{itemize}
  \item Graduated First Class.
  \item Final project focused on computational modelling of solvated molecules.
\end{itemize}

\cvsection{Achievements}
\begin{itemize}
  \item Lead the winning team at the Lloyds Reboot Hackathon — London 2025
  \item Emerging Talent in Tech — Women's ConnecTech (Shortlisted)
  \item Game Changers Awards — Nominated for 2 awards
\end{itemize}

\cvsection{Certifications}
\begin{itemize}
  \item GCP Digital Cloud Leader — Google Cloud, 2024
  \item Professional Scrum Master I — 2024
  \item Level 4 Software Engineering Apprenticeship — Distinction
\end{itemize}


\cvsection{Skills}
\cvtag{React} \cvtag{TypeScript} \cvtag{JavaScript} \cvtag{styled-components}
\cvtag{Express.js} \cvtag{Postgres} \cvtag{SQL} \cvtag{Python}
\cvtag{Docker} \cvtag{Kubernetes} \cvtag{Terraform} \cvtag{Linux/Bash}
\cvtag{CI/CD (Jenkins, Harness)} \cvtag{Git/GitHub}
\cvtag{Cloud (Google Cloud, Azure basics)}
\cvtag{AI Agents / RAG}
\cvtag{Testing (Jest, Playwright, Cypress)}

\end{paracol}
\end{document}